\section{Conclusion}

This paper documents a clear firm-size wage premium in Colombia. The descriptive
evidence shows that real hourly wages rise sharply with firm size: workers in
firms with 101 or more employees earn more than two and a half times the average
hourly income of solo workers. The same descriptive evidence also shows why the
premium is macroeconomically relevant. About two thirds of worker-years are
concentrated in solo work and firms with up to ten workers, while the
intermediate firm-size categories account for a relatively small share of
employment. This employment structure means that the firm-size wage premium is
not only a wage-regression fact; it is also a fact about where workers are
located in the productive structure.

The regression results show that a substantial conditional premium remains after
controlling for gender, education, formality, and sector-year fixed effects. In
the full specification, the premium for workers in firms with 101 or more
employees is about 35 percent relative to solo workers, and all firm-size
categories above solo work have positive and statistically significant premiums.
At the same time, the reduction in the 101+ coefficient from 1.017 log points in
the raw specification to 0.299 log points in the full specification indicates
that formality, observable skills, and sector-year composition explain a large
share of the raw gap.

These findings are relevant beyond wage inequality. In a labor market with high
informality and a large share of employment in solo work and very small firms,
the firm-size wage premium is also a diagnostic of efficiency and potential
misallocation. If larger firms are more productive or provide better matches,
then barriers that keep workers and firms from scaling may have aggregate
consequences. If the premium mainly reflects sorting of more educated and formal
workers into larger firms, the policy problem is more directly one of worker
mobility, skills, and formalization. In both cases, the evidence cautions against
policies that simply preserve smallness. A more appropriate policy agenda would
combine productivity growth in small and medium firms, lower barriers to
formalization and firm growth, and stronger pathways for workers to move toward
more productive employers.

This interpretation connects the paper to a broader policy agenda for Colombia.
If growth and equity depend on changing the way production is organized
\citep{eslava2026crecimiento}, then the firm-size wage premium is useful because
it reveals where the wage gains from that transformation are likely to appear:
in the movement from solo work and micro-firms toward more productive, formal,
and scalable employers. The policy implication is not to favor large firms per
se, but to remove the barriers that keep productive small firms from growing and
workers from accessing better matches. That agenda includes reducing regulatory
and tax distortions that penalize firm growth, strengthening productivity and
innovation policy, improving access to skills and finance, and designing
formalization policies that expand rather than restrict quality employment.

Future versions of the paper should extend the analysis with region, occupation,
and worker-age controls, and should explore whether the premium is stronger in
sectors where productivity dispersion or informality is larger. The strongest
test of the misallocation interpretation would link household-survey wage
patterns to firm-level measures of value added, capital, and employment, allowing
the analysis to distinguish wage premia due to sorting from premia associated
with differences in firm productivity.
