\section{Discussion}
 
Our central finding is a sizable firm-size wage premium that survives controls for gender, education, and sector, and that persists even after we condition on formality status. While the magnitude of the premium is broadly consistent with the existing Latin American evidence \citep{Schaffner1998, AlvarezBenguriaEngbomMoser2018, GerardLagosSeverniniCard2021}, the persistence of the premium even after controling for the formality status is, we argue, the more substantively informative feature of our results. In this section we discuss what such a premium can and cannot tell us about the underlying economic mechanisms.
 
A long-standing concern in the developing-country literature is that the apparent firm-size premium is, at least in part, a relabeling of the formal--informal wage gap. In dual labor market models in the tradition of \citet{HarrisTodaro1970} and \citet{Fields1975}, large firms are disproportionately formal, and formality itself carries a wage premium through some combination of higher productivity, mandated benefits, payroll taxation, and selection. From this perspective, much of what is conventionally labeled a ``firm-size'' premium may simply reflect the boundary between the formal and informal sectors rather than any return to firm scale per se, as formal firms tend to be also larger. By showing that the premium remains after conditioning on formality, our estimates indicate that this dual-market channel is not the whole story: even among workers of the same formality status, larger employers pay more. In this respect our findings reinforce \citet{Schaffner1998} and complement the matched employer--employee evidence from Brazil \citep{AlvarezBenguriaEngbomMoser2018, GerardLagosSeverniniCard2021, EngbomMoser2022} and Costa Rica \citep{AlfaroUrenaManeliciVasquez2022}, all of which point toward firm-specific pay determination as a first-order feature of Latin American labor markets.
 
What our controls \textit{cannot} do is distinguish among other leading explanations for the premium. As \citet{BrownMedoff1989} and \citet{OiIdson1999} emphasized for the United States, a premium that survives observable controls is consistent with several non-exclusive mechanisms. The first is \textit{unobserved worker quality}: gender, schooling, and sector capture only a slice of productive heterogeneity, leaving non-cognitive skills, school quality, and unmeasured ability bundled into the firm-size coefficient. \citet{SoderbomTealWambugu2005} show that this channel can be quantitatively important in Kenya and Ghana, where panel-data identification absorbs much of the cross-sectional premium into a worker fixed effect. The second is \textit{rent-sharing}: larger firms tend to be more productive, more capital-intensive, and more exposed to product-market power, and they may share part of those rents with workers through bargaining, fair-wage norms, or hold-up considerations. The matched-data literature beginning with \citet{AbowdKramarzMargolis1999} and \citet{CardHeiningKline2013}, and extended to the U.S. by \citet{Song2019}, has shown that firm-specific pay premia account for a quantitatively important share of wage variation in advanced economies; the Brazilian evidence cited above extends this conclusion to Latin America. A third possibility is \textit{efficiency-wage} or monitoring-cost reasoning, in which larger firms face greater difficulty observing individual effort and pay above-market wages to elicit it. Because our identification rests on observables, we cannot adjudicate among these mechanisms, and we are careful not to interpret the surviving coefficient as a pure rent-sharing parameter.
 
One reading we explicitly do \textit{not} draw is a monopsony interpretation. Standard monopsony models predict the opposite sign: employers with greater wage-setting power should pay \textit{less} relative to marginal product, not more \citep{Card2022}. A positive, robust firm-size premium is therefore most naturally interpreted as evidence against a simple monopsony story and in favor of productivity-driven, rent-sharing, or sorting-based mechanisms, consistent with the firm-centric view of wage determination that has emerged in the recent literature.
 
Several limitations follow from this discussion. Because our identification rests on observables, we cannot separate the unoobserved worker-quality channel from the firm-rent channel; doing so would require either matched employer--employee data with worker mobility, in the spirit of \citet{AbowdKramarzMargolis1999} and \citet{CardHeiningKline2013}, or a source of plausibly exogenous variation in firm-size exposure. Similarly, while controlling for formality rules out a mechanical formal--informal explanation, it does not rule out that the premium reflects firm characteristics correlated with both size and pay-setting capacity---capital intensity, exporter status, or foreign ownership, among others---which our data do not allow us to isolate. These extensions are natural next steps. In the meantime, our results contribute to a growing body of evidence that the firm-size wage premium in Latin America is economically meaningful, robust to standard observable controls, and---importantly---not reducible to the formal--informal margin.