\section{Introduction}

Large firms tend to pay higher wages than small firms. This empirical regularity, usually known as the firm-size wage premium, is one of the classic facts in labor economics. Its interpretation, however, is not mechanical. The premium may reflect worker sorting, monitoring costs, efficiency wages, rent sharing, or productivity differences across firms \citep{brown1989employer,oi1999firm,troske1999evidence}. The matched employer-employee literature further shows that wages reflect both worker heterogeneity and firm wage-setting heterogeneity \citep{abowd1999high,card2013workplace,song2019firming}.

The firm-size wage premium has implications not only for wage inequality but also for allocative efficiency, and the connection between the two depends on what the premium reflects. An older reading, anchored by panel
evidence from \citet{SoderbomTealWambugu2005} for Kenya and Ghana, attributed much of the cross-sectional firm-size premium in developing countries to unobserved worker quality rather than firm-side pay setting; under that reading, reallocating workers across firm sizes would not raise
aggregate output. More recent matched employer--employee work has shifted the interpretation. Mover designs in the tradition of \citet{AbowdKramarzMargolis1999} and \citet{CardHeiningKline2013} consistently find that firm-specific pay premia survive controls for
worker fixed effects---in the United States \citep{Song2019}, in Brazil \citep{AlvarezBenguriaEngbomMoser2018, GerardLagosSeverniniCard2021, EngbomMoser2022}, and in Costa Rica \citep{AlfaroUrenaManeliciVasquez2022}---ruling out a pure sorting interpretation of the premium even in middle-income labor markets. To the extent that these firm pay premia reflect underlying productivity differences across firms---through management practices, capital intensity, or technology \citep{Bloom2019}---transmitted to workers through rent-sharing of productive quasi-rents \citep{Card2022}, the allocation of employment across firm sizes shapes aggregate productivity. A persistent firm-size premium combined with a large share of workers in solo work and micro-firms is then the empirical signature of a labor market in which workers and firms are not freely reallocating toward more productive matches---the central diagnostic of the misallocation literature \citep{restuccia2008policy, hsieh2009misallocation}. The relevant empirical object is therefore not only the slope of wages with respect to firm size, but also the mass of workers located at each point
of that distribution: a steep premium is more consequential in a labor market where most employment is concentrated in solo work and micro-firms than in one where small firms represent a thin margin.

Colombia is a natural setting in which to study this question. The country
combines a highly heterogeneous productive structure with a large informal
sector, strong differences between small and large firms, and persistent wage
inequality. Existing Colombian work has studied wage differentials by sector and
firm characteristics in the formal labor market \citep{iregui2012diferenciales},
but there is little systematic evidence on the firm-size wage premium using
nationally representative household survey data over a long period. This gap
matters because firm size is closely connected to formality, access to
technology, managerial capacity, regulatory compliance, and the allocation of
workers across the productive structure.

This motivation is closely related to the recent policy diagnosis in
\citet{eslava2026crecimiento}. They argue that growth and equity in Colombia are
not competing objectives, but joint outcomes of productive transformation. In
their diagnosis, low-income households are disproportionately linked to
own-account work, very small businesses, informality, and jobs with low earnings,
whereas higher-income households are more likely to be connected to larger and
more formal employers. The implication is that the organization of production is
itself a mechanism through which inequality and low aggregate productivity are
jointly reproduced. Our paper provides microeconometric evidence on one central
component of that mechanism: the wage gradient associated with firm size.

This paper documents the firm-size wage premium in Colombia using harmonized
microdata from the Gran Encuesta Integrada de Hogares (GEIH) for 2008--2019 and
2021--2025. The central question is descriptive and econometric: do workers in
larger firms earn higher real hourly labor income than comparable workers in solo
work or smaller firms, and how much of the raw gradient remains after accounting
for observable worker characteristics, formality, and sector-year conditions?
The resulting estimates are conditional wage gaps, not causal effects of firm
size. They are nevertheless informative because persistent conditional gaps in a
labor market with concentrated micro-firm employment are a natural diagnostic of
segmentation and possible allocative frictions.

The contribution is fourfold. First, we construct a comparable firm-size
classification across changes in the GEIH questionnaire, including a harmonized
``101+'' category for the largest firms. Second, we show that Colombia's
employment structure is polarized: employment is heavily concentrated in solo
work and firms with up to ten workers, the intermediate firm-size categories are
thin, and the largest category accounts for a sizeable minority of employment.
Third, we document the wage gradient in both pooled data and the 2008--2025
endpoints, showing that the large-firm advantage remains economically important
over time. Fourth, we estimate conditional firm-size wage premiums, dynamic
premium paths, and a formal trend test. The estimates should be interpreted as
conditional wage gaps rather than causal effects of working in a larger firm, but
they provide a useful diagnostic of wage inequality, labor-market segmentation,
and potential allocative frictions in Colombia.
