\section{Methodology}

\subsection{Descriptive Premiums}

We begin by documenting the raw firm-size gradient in real hourly labor income.
For each firm-size group \(g\) and year \(t\), we compute the weighted mean:

\[
  \bar{w}_{gt} =
  \frac{\sum_{i \in (g,t)} fex_{it} w_{it}^{real}}
       {\sum_{i \in (g,t)} fex_{it}},
\]

where \(fex_{it}\) is the GEIH expansion factor. We also compute the employment
share of each firm-size group:

\[
  s_{gt} =
  \frac{\sum_{i \in (g,t)} fex_{it}}
       {\sum_{i \in t} fex_{it}}.
\]

These two objects are used in the descriptive tables and figures. The main
comparison figures plot the employment distribution and mean real hourly labor
income by firm size in 2008 and 2025, while appendix figures report the full
time path of employment shares and raw premiums. For the comparison between 2008
and 2025, the descriptive difference for group \(g\) is:

\[
  Diff_g = 100 \times
  \left(\frac{\bar{w}_{g,2025}}{\bar{w}_{g,2008}} - 1\right).
\]

\subsection{Econometric Specification}

The main econometric exercise estimates the conditional firm-size wage premium
in a log-wage model. The baseline specification is:

\[
  \ln(w_{ist}) =
  \alpha
  + \sum_{g \neq g_0} \beta_g \mathbf{1}\{Size_{ist}=g\}
  + X_{ist}'\gamma
  + \lambda_{s \times t}
  + \varepsilon_{ist},
\]

where \(w_{ist}\) is real hourly labor income for worker \(i\) in sector \(s\) in year \(t\), \(Size_{ist}\) is the harmonized firm-size category, and \(g_0\) is the reference group. We use solo workers as the reference category. This choice makes the coefficient path directly interpretable as the wage premium associated with moving from individual work to increasingly larger firms. Because solo workers may combine self-employment and very small-scale wage employment, we interpret the estimates as conditional gaps relative to the bottom of the firm-size distribution rather than as pure firm effects.

The vector \(X_{ist}\) includes a female-worker indicator, age, age squared,
education dummies, and a formal-employment indicator. The fixed effect
\(\lambda_{s \times t}\)
absorbs sector-year conditions, allowing each broad sector to have its own wage
level in each year. This is important because large firms are not randomly
distributed across sectors, and sectoral shocks may be correlated with both wages
and firm size. The model is estimated with GEIH expansion weights, and standard
errors are clustered by sector.

City fixed effects would be a useful additional robustness check because they
would absorb persistent differences across local labor markets. We do not
estimate that specification in this version because the harmonized file used for
the regressions does not yet preserve a consistent city identifier.

In the results table, we report four nested specifications. The first column
includes only firm-size indicators. The second adds sector-year fixed effects.
The third adds gender, age, age squared, and education controls, but excludes
formality. The fourth adds formality. Comparing the third and fourth columns
shows how much of the
firm-size gradient is absorbed by differences in formal employment across firm
sizes.

The coefficients \(\beta_g\) are log-point differences relative to solo workers.
For interpretation, we transform them into percentage premiums:

\[
  Premium_g = 100 \times \left(\exp(\hat{\beta}_g)-1\right).
\]



\subsection{Dynamic Premiums and Trend Test}

The same framework can be extended to study the evolution of the premium over
time by interacting firm-size categories with year indicators:

\[
  \ln(w_{ist}) =
  \alpha
  + \sum_{\tau}\sum_{g \neq g_0}
    \beta_{g\tau}\mathbf{1}\{Size_{ist}=g\}\mathbf{1}\{Year_{t}=\tau\}
  + X_{ist}'\gamma
  + \lambda_{s \times t}
  + \varepsilon_{ist}.
\]

This dynamic specification produces a sequence of firm-size premiums by year and
can be used to assess whether the premium has widened, narrowed, or remained
stable. We also estimate a more parsimonious trend specification:

\[
  \ln(w_{ist}) =
  \alpha
  + \sum_{g \neq g_0} \beta_g\mathbf{1}\{Size_{ist}=g\}
  + \sum_{g \neq g_0} \delta_g
    \mathbf{1}\{Size_{ist}=g\}Trend_t
  + X_{ist}'\gamma
  + \lambda_{s \times t}
  + \varepsilon_{ist},
\]

where \(Trend_t\) is a linear year trend normalized to zero in 2008. The
parameter \(\delta_g\) tests whether the wage premium for firm-size group \(g\)
increased over time relative to solo workers. We report one-sided tests of
\(H_0:\delta_g=0\) against \(H_1:\delta_g>0\), because the empirical question is
whether the premium widened over the period.
